environmental_data_preperation

### 2018-11-13 src/env_data_prep.Rmd
removing some test scripts i no longer need, plus data exploration pt 2

A note to anyone who might happen to stumble across this... I am a beginner in R and have had no exposure to similar languages. I don't know what I'm doing. The code herein is unlikely to be elegant and there area probably more efficient ways of running the code.

@@

    }
}
```

>>>>

A note to anyone who might happen to stumble across this... I am a beginner in R and have had no exposure to similar languages. I don't know what I'm doing. The code herein is unlikely to be elegant and there are probably more efficient ways of running the code.

@@

    }
}
```
note that if you wanted to just loop through the netcdfs and create a ton of raster bricks with the same name as the netcdf, the following code you wrote before works

netcdf_list <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = TRUE) #true means the full path is included
no_netcdf <- length(netcdf_list) #for the loop - need to know how many files to cycle through
netcdf_name <- list.files("../data/env/netcdf", pattern = '*.nc', full.names = FALSE) #false means the path is not included
library (ncdf4)
for (i in 1:no_netcdf) {
  print(netcdf_name[i]) #this just prings the name of the netCDF R is working on
  temp_brick <- brick(netcdf_list[i], lvar = 4)
  temp_brick <- projectRaster(temp_brick, aea) #aea is an existing raster in the projection I want that I created (environmental_data_preperation)
  assign(netcdf_name[i], temp_brick) #this asigns the netCDF name to the raster brick
}
